Evidence for a Third Color Parameter Within the Type~Ia Supernovae of the Nearby Supernova Factory

### 2018-05-17 submit/fix.tex
residuals given one fixed

@@

@@

5.48e-07 & -1.77e-06 & 3.87e-07 & -1.63e-05 & 2.14e-04 & -2.59e-04 & 3.59e-06 & 4.51e-07 & -1.46e-06 & 3.12e-07 & -1.32e-05 & 2.60e-04 & -1.34e-04 & 2.78e-06 & 3.58e-07 & -1.16e-06 & 2.40e-07 & -1.04e-05 & 1.90e-04 & -5.51e-05 & 1.70e-06 & 2.87e-07 & -9.20e-07 & 1.88e-07 & -8.14e-06 & 1.09e-04 & -1.66e-05 & 1.05e-06 & 2.24e-07 & -7.21e-07 & 1.43e-07 & -6.30e-06 & -3.58e-05 & -6.71e-06 & 4.73e-07 \\
-1.77e-06 & 2.70e-05 & -2.60e-06 & 1.85e-04 & -4.04e-03 & -3.01e-03 & -1.78e-05 & -1.45e-06 & 2.18e-05 & -2.12e-06 & 1.49e-04 & -3.25e-03 & -2.66e-03 & -1.43e-05 & -1.14e-06 & 1.72e-05 & -1.59e-06 & 1.17e-04 & -2.58e-03 & -2.14e-03 & -1.00e-05 & -9.23e-07 & 1.40e-05 & -1.22e-06 & 9.43e-05 & -2.01e-03 & -1.63e-03 & -7.87e-06 & -7.31e-07 & 1.14e-05 & -8.85e-07 & 7.62e-05 & -1.09e-03 & -1.17e-03 & -5.25e-06 \\
3.87e-07 & -2.60e-06 & 1.26e-06 & -2.22e-05 & 3.88e-04 & 1.66e-03 & 1.04e-05 & 3.23e-07 & -2.15e-06 & 1.02e-06 & -1.82e-05 & 4.99e-04 & 1.38e-03 & 8.28e-06 & 2.38e-07 & -1.47e-06 & 7.79e-07 & -1.31e-05 & 5.44e-04 & 1.02e-03 & 6.05e-06 & 1.86e-07 & -1.12e-06 & 6.13e-07 & -1.01e-05 & 4.13e-04 & 8.00e-04 & 4.56e-06 & 1.39e-07 & -8.12e-07 & 4.67e-07 & -7.36e-06 & 1.56e-04 & 5.93e-04 & 3.15e-06 \\
-1.63e-05 & 1.85e-04 & -2.22e-05 & 1.57e-03 & -2.93e-02 & -1.45e-02 & -2.66e-04 & -1.33e-05 & 1.50e-04 & -1.80e-05 & 1.27e-03 & -2.77e-02 & -1.31e-02 & -2.13e-04 & -1.04e-05 & 1.17e-04 & -1.36e-05 & 9.90e-04 & -2.33e-02 & -1.02e-02 & -1.52e-04 & -8.29e-06 & 9.49e-05 & -1.05e-05 & 7.94e-04 & -1.77e-02 & -7.72e-03 & -1.16e-04 & -6.36e-06 & 7.71e-05 & -7.70e-06 & 6.34e-04 & -8.10e-03 & -4.86e-03 & -7.93e-05 \\
2.14e-04 & -4.04e-03 & 3.88e-04 & -2.93e-02 & 6.88e+00 & 1.25e+00 & 6.67e-03 & 1.42e-04 & -2.96e-03 & 3.19e-04 & -2.17e-02 & 5.55e+00 & 1.07e+00 & 5.15e-03 & 9.62e-05 & -2.17e-03 & 2.27e-04 & -1.62e-02 & 4.46e+00 & 9.67e-01 & 3.67e-03 & 6.03e-05 & -1.67e-03 & 1.74e-04 & -1.27e-02 & 3.66e+00 & 8.52e-01 & 3.02e-03 & 3.86e-05 & -1.42e-03 & 1.29e-04 & -1.09e-02 & 2.89e+00 & 6.67e-01 & 2.09e-03 \\
-2.59e-04 & -3.01e-03 & 1.66e-03 & -1.45e-02 & 1.25e+00 & 1.73e+01 & 8.74e-03 & -1.90e-04 & -2.82e-03 & 1.32e-03 & -1.33e-02 & 1.09e+00 & 1.44e+01 & 7.09e-03 & -1.66e-04 & -1.50e-03 & 9.73e-04 & -6.78e-03 & 1.84e+00 & 1.15e+01 & 4.92e-03 & -1.22e-04 & -1.02e-03 & 7.56e-04 & -4.36e-03 & 1.63e+00 & 9.61e+00 & 3.16e-03 & -9.95e-05 & -3.83e-04 & 5.60e-04 & -7.65e-04 & 1.36e+00 & 7.93e+00 & 1.78e-03 \\
3.59e-06 & -1.78e-05 & 1.04e-05 & -2.66e-04 & 6.67e-03 & 8.74e-03 & 2.83e-04 & 2.89e-06 & -1.38e-05 & 8.38e-06 & -2.14e-04 & 1.06e-02 & 6.79e-03 & 2.29e-04 & 1.97e-06 & -9.39e-06 & 6.36e-06 & -1.60e-04 & 1.09e-02 & 4.07e-03 & 1.76e-04 & 1.38e-06 & -7.40e-06 & 4.92e-06 & -1.23e-04 & 7.97e-03 & 3.03e-03 & 1.41e-04 & 9.17e-07 & -7.22e-06 & 3.61e-06 & -9.91e-05 & 2.61e-03 & 2.30e-03 & 1.08e-04 \\
4.51e-07 & -1.45e-06 & 3.23e-07 & -1.33e-05 & 1.42e-04 & -1.90e-04 & 2.89e-06 & 3.98e-07 & -1.28e-06 & 2.69e-07 & -1.13e-05 & 1.97e-04 & -2.55e-05 & 2.25e-06 & 3.23e-07 & -1.04e-06 & 2.11e-07 & -9.09e-06 & 1.44e-04 & 4.26e-05 & 1.25e-06 & 2.58e-07 & -8.18e-07 & 1.66e-07 & -7.11e-06 & 7.38e-05 & 5.08e-05 & 6.94e-07 & 1.88e-07 & -6.00e-07 & 1.23e-07 & -5.27e-06 & -5.22e-05 & 9.50e-06 & 2.40e-07 \\
-1.46e-06 & 2.18e-05 & -2.15e-06 & 1.50e-04 & -2.96e-03 & -2.82e-03 & -1.38e-05 & -1.28e-06 & 1.93e-05 & -1.77e-06 & 1.30e-04 & -2.43e-03 & -2.99e-03 & -1.18e-05 & -1.04e-06 & 1.56e-05 & -1.35e-06 & 1.05e-04 & -1.96e-03 & -2.59e-03 & -7.61e-06 & -8.41e-07 & 1.25e-05 & -1.05e-06 & 8.38e-05 & -1.49e-03 & -1.96e-03 & -5.57e-06 & -6.24e-07 & 9.33e-06 & -7.68e-07 & 6.29e-05 & -7.66e-04 & -1.11e-03 & -4.00e-06 \\
3.12e-07 & -2.12e-06 & 1.02e-06 & -1.80e-05 & 3.19e-04 & 1.32e-03 & 8.38e-06 & 2.69e-07 & -1.77e-06 & 8.55e-07 & -1.50e-05 & 4.09e-04 & 1.11e-03 & 6.69e-06 & 2.02e-07 & -1.23e-06 & 6.67e-07 & -1.10e-05 & 4.43e-04 & 8.16e-04 & 4.94e-06 & 1.57e-07 & -9.42e-07 & 5.21e-07 & -8.46e-06 & 3.37e-04 & 6.40e-04 & 3.75e-06 & 1.14e-07 & -6.87e-07 & 3.81e-07 & -6.16e-06 & 1.31e-04 & 4.77e-04 & 2.65e-06 \\
-1.32e-05 & 1.49e-04 & -1.82e-05 & 1.27e-03 & -2.17e-02 & -1.33e-02 & -2.14e-04 & -1.13e-05 & 1.30e-04 & -1.50e-05 & 1.10e-03 & -2.15e-02 & -1.35e-02 & -1.75e-04 & -9.01e-06 & 1.04e-04 & -1.15e-05 & 8.72e-04 & -1.85e-02 & -1.11e-02 & -1.24e-04 & -7.18e-06 & 8.32e-05 & -8.95e-06 & 6.92e-04 & -1.39e-02 & -8.33e-03 & -9.24e-05 & -5.25e-06 & 6.25e-05 & -6.56e-06 & 5.15e-04 & -5.96e-03 & -4.09e-03 & -6.74e-05 \\
2.60e-04 & -3.25e-03 & 4.99e-04 & -2.77e-02 & 5.55e+00 & 1.09e+00 & 1.06e-02 & 1.97e-04 & -2.43e-03 & 4.09e-04 & -2.15e-02 & 5.14e+00 & 9.38e-01 & 8.36e-03 & 1.44e-04 & -1.81e-03 & 3.04e-04 & -1.65e-02 & 4.30e+00 & 8.58e-01 & 5.98e-03 & 9.79e-05 & -1.38e-03 & 2.32e-04 & -1.28e-02 & 3.43e+00 & 7.80e-01 & 4.61e-03 & 5.79e-05 & -1.14e-03 & 1.72e-04 & -1.02e-02 & 2.35e+00 & 6.50e-01 & 3.24e-03 \\
-1.34e-04 & -2.66e-03 & 1.38e-03 & -1.31e-02 & 1.07e+00 & 1.44e+01 & 6.79e-03 & -2.55e-05 & -2.99e-03 & 1.11e-03 & -1.35e-02 & 9.38e-01 & 1.37e+01 & 6.42e-03 & 1.80e-05 & -2.22e-03 & 8.57e-04 & -1.08e-02 & 1.49e+00 & 1.16e+01 & 1.63e-03 & 1.96e-05 & -1.57e-03 & 6.72e-04 & -7.66e-03 & 1.31e+00 & 9.54e+00 & 3.93e-06 & -2.30e-05 & -5.99e-04 & 5.06e-04 & -3.06e-03 & 1.08e+00 & 7.15e+00 & -1.30e-03 \\
2.78e-06 & -1.43e-05 & 8.28e-06 & -2.13e-04 & 5.15e-03 & 7.09e-03 & 2.29e-04 & 2.25e-06 & -1.18e-05 & 6.69e-06 & -1.75e-04 & 8.36e-03 & 6.42e-03 & 1.94e-04 & 1.57e-06 & -8.81e-06 & 5.16e-06 & -1.35e-04 & 8.63e-03 & 4.45e-03 & 1.50e-04 & 1.09e-06 & -6.98e-06 & 4.01e-06 & -1.05e-04 & 6.28e-03 & 3.21e-03 & 1.19e-04 & 6.68e-07 & -6.26e-06 & 2.97e-06 & -8.31e-05 & 2.07e-03 & 1.95e-03 & 8.89e-05 \\
3.58e-07 & -1.14e-06 & 2.38e-07 & -1.04e-05 & 9.62e-05 & -1.66e-04 & 1.97e-06 & 3.23e-07 & -1.04e-06 & 2.02e-07 & -9.01e-06 & 1.44e-04 & 1.80e-05 & 1.57e-06 & 2.82e-07 & -9.34e-07 & 1.66e-07 & -7.83e-06 & 9.39e-05 & 1.01e-04 & 6.81e-07 & 2.27e-07 & -7.44e-07 & 1.30e-07 & -6.18e-06 & 3.58e-05 & 8.41e-05 & 2.43e-07 & 1.67e-07 & -5.47e-07 & 9.84e-08 & -4.62e-06 & -6.31e-05 & 3.16e-05 & -5.49e-08 \\
-1.16e-06 & 1.72e-05 & -1.47e-06 & 1.17e-04 & -2.17e-03 & -1.50e-03 & -9.39e-06 & -1.04e-06 & 1.56e-05 & -1.23e-06 & 1.04e-04 & -1.81e-03 & -2.22e-03 & -8.81e-06 & -9.34e-07 & 1.41e-05 & -9.72e-07 & 9.37e-05 & -1.32e-03 & -2.18e-03 & -5.00e-06 & -7.59e-07 & 1.15e-05 & -7.50e-07 & 7.59e-05 & -9.56e-04 & -1.55e-03 & -3.43e-06 & -5.69e-07 & 8.69e-06 & -5.57e-07 & 5.80e-05 & -4.18e-04 & -8.99e-04 & -2.79e-06 \\
2.40e-07 & -1.59e-06 & 7.79e-07 & -1.36e-05 & 2.27e-04 & 9.73e-04 & 6.36e-06 & 2.11e-07 & -1.35e-06 & 6.67e-07 & -1.15e-05 & 3.04e-04 & 8.57e-04 & 5.16e-06 & 1.66e-07 & -9.72e-07 & 5.47e-07 & -8.75e-06 & 3.25e-04 & 6.57e-04 & 3.71e-06 & 1.30e-07 & -7.44e-07 & 4.31e-07 & -6.79e-06 & 2.47e-04 & 5.11e-04 & 2.81e-06 & 9.40e-08 & -5.37e-07 & 3.18e-07 & -4.97e-06 & 9.24e-05 & 3.58e-04 & 1.99e-06 \\
-1.04e-05 & 1.17e-04 & -1.31e-05 & 9.90e-04 & -1.62e-02 & -6.78e-03 & -1.60e-04 & -9.09e-06 & 1.05e-04 & -1.10e-05 & 8.72e-04 & -1.65e-02 & -1.08e-02 & -1.35e-04 & -7.83e-06 & 9.37e-05 & -8.75e-06 & 7.76e-04 & -1.38e-02 & -1.03e-02 & -9.19e-05 & -6.28e-06 & 7.58e-05 & -6.80e-06 & 6.24e-04 & -1.01e-02 & -7.01e-03 & -6.68e-05 & -4.66e-06 & 5.77e-05 & -5.07e-06 & 4.74e-04 & -4.00e-03 & -3.86e-03 & -5.10e-05 \\
1.90e-04 & -2.58e-03 & 5.44e-04 & -2.33e-02 & 4.46e+00 & 1.84e+00 & 1.09e-02 & 1.44e-04 & -1.96e-03 & 4.43e-04 & -1.85e-02 & 4.30e+00 & 1.49e+00 & 8.63e-03 & 9.39e-05 & -1.32e-03 & 3.25e-04 & -1.38e-02 & 3.99e+00 & 1.20e+00 & 6.47e-03 & 5.76e-05 & -9.90e-04 & 2.49e-04 & -1.06e-02 & 3.20e+00 & 1.04e+00 & 4.99e-03 & 2.60e-05 & -7.80e-04 & 1.84e-04 & -8.18e-03 & 2.21e+00 & 8.94e-01 & 3.63e-03 \\
-5.51e-05 & -2.14e-03 & 1.02e-03 & -1.02e-02 & 9.67e-01 & 1.15e+01 & 4.07e-03 & 4.26e-05 & -2.59e-03 & 8.16e-04 & -1.11e-02 & 8.58e-01 & 1.16e+01 & 4.45e-03 & 1.01e-04 & -2.18e-03 & 6.57e-04 & -1.03e-02 & 1.20e+00 & 1.04e+01 & -3.81e-04 & 8.39e-05 & -1.55e-03 & 5.18e-04 & -7.33e-03 & 1.05e+00 & 8.61e+00 & -1.61e-03 & 2.13e-05 & -6.03e-04 & 3.97e-04 & -3.07e-03 & 8.81e-01 & 6.41e+00 & -2.52e-03 \\
1.70e-06 & -1.00e-05 & 6.05e-06 & -1.52e-04 & 3.67e-03 & 4.92e-03 & 1.76e-04 & 1.25e-06 & -7.61e-06 & 4.94e-06 & -1.24e-04 & 5.98e-03 & 1.63e-03 & 1.50e-04 & 6.81e-07 & -5.00e-06 & 3.71e-06 & -9.19e-05 & 6.47e-03 & -3.81e-04 & 1.30e-04 & 3.89e-07 & -4.13e-06 & 2.87e-06 & -7.16e-05 & 4.86e-03 & -3.90e-04 & 1.06e-04 & 2.10e-07 & -4.36e-06 & 2.13e-06 & -5.81e-05 & 1.91e-03 & 6.81e-04 & 8.25e-05 \\

>>>>

\added{
\begin{equation}
\begin{pmatrix}
\small
\begin{array}{rrrrrrr}
EW_{\mathrm{Ca}} & 7.0  \pm 0.5 \times 10^{ 2} & 6.7  \pm 0.3 \times 10^{ 2} & 3.7  \pm 1.1 \times 10^{ 2} & 3.3  \pm 6.2 \times 10^{ 1} & 7.7  \pm 17.0 \times 10^{ 0} & 6.3  \pm 11.2 \times 10^{ 1} \\
5.0  \pm 0.2 \times 10^{ 1} & EW_{\mathrm{Si}} & 4.9  \pm 0.2 \times 10^{ 1} & 2.5  \pm 0.2 \times 10^{ 0} & 4.7  \pm 3.3 \times 10^{ 0} & 1.2  \pm 1.5 \times 10^{ 0} & 1.1  \pm 1.2 \times 10^{ 1} \\
3.8  \pm 0.2 \times 10^{ 2} & 3.9  \pm 0.2 \times 10^{ 2} & \lambda_{\mathrm{Si}} & 1.4  \pm 0.3 \times 10^{ 2} & 7.4  \pm 8.8 \times 10^{ 1} & 4.3  \pm 6.8 \times 10^{ 1} & 4.5  \pm 7.0 \times 10^{ 1} \\
9.9  \pm 0.4 \times 10^{-1} & 2.9  \pm 0.2 \times 10^{-1} & 9.7  \pm 0.4 \times 10^{-1} & x_1 & 5.2  \pm 1.4 \times 10^{-1} & 2.3  \pm 1.6 \times 10^{-1} & 6.7  \pm 2.3 \times 10^{-1} \\
5.4  \pm 0.5 \times 10^{-3} & 5.4  \pm 0.5 \times 10^{-3} & 5.4  \pm 0.5 \times 10^{-3} & 5.4  \pm 0.5 \times 10^{-3} & E_{\gamma^0}({\hat{B}}-{\hat{V}})& 5.4  \pm 0.5 \times 10^{-3} & 5.4  \pm 0.5 \times 10^{-3} \\
1.5  \pm 0.3 \times 10^{-3} & 1.4  \pm 0.3 \times 10^{-3} & 1.5  \pm 0.3 \times 10^{-3} & 1.5  \pm 0.3 \times 10^{-3} & 1.5  \pm 0.3 \times 10^{-3} &  E_{\gamma^1}({\hat{B}}-{\hat{V}}) & 1.5  \pm 0.3 \times 10^{-3} \\
2.6  \pm 1.1 \times 10^{-3} & 2.6  \pm 1.1 \times 10^{-3} & 2.6  \pm 1.1 \times 10^{-3} & 2.6  \pm 1.1 \times 10^{-3} & 2.6  \pm 1.1 \times 10^{-3} & 2.6  \pm 1.1 \times 10^{-3} & A_{p,V} \\
\end{array}
\end{pmatrix}.
\label{ellipse:eqn}
\end{equation}
}

@@

\added{The following is the  covariance matrix for the global cofactors $\{ \alpha_{\hat{U}}, \beta_{\hat{U}}, \eta_{\hat{U}}, \zeta_{\hat{U}}, \gamma^0_{\hat{U}},\gamma^1_{\hat{U}}, \sigma_p \phi_{\hat{U}}, 
\ldots,
\alpha_{\hat{I}}, \beta_{\hat{I}}, \eta_{\hat{I}}, \zeta_{\hat{I}}, \gamma^0_{\hat{I}},\gamma^1_{\hat{I}}, \sigma_p \phi_{\hat{I}}
 \}$.  The matrix 35x35 is big so will have to go in supplemental material.}

@@

5.5\times 10^{-7} & -1.8\times 10^{-6} & 3.9\times 10^{-7} & -1.6\times 10^{-5} & 2.1\times 10^{-4} & -2.6\times 10^{-4} & 3.6\times 10^{-6} & 4.5\times 10^{-7} & -1.5\times 10^{-6} & 3.1\times 10^{-7} & -1.3\times 10^{-5} & 2.6\times 10^{-4} & -1.3\times 10^{-4} & 2.8\times 10^{-6} & 3.6\times 10^{-7} & -1.2\times 10^{-6} & 2.4\times 10^{-7} & -1.0\times 10^{-5} & 1.9\times 10^{-4} & -5.5\times 10^{-5} & 1.7\times 10^{-6} & 2.9\times 10^{-7} & -9.2\times 10^{-7} & 1.9\times 10^{-7} & -8.1\times 10^{-6} & 1.1\times 10^{-4} & -1.7\times 10^{-5} & 1.1\times 10^{-6} & 2.2\times 10^{-7} & -7.2\times 10^{-7} & 1.4\times 10^{-7} & -6.3\times 10^{-6} & -3.6\times 10^{-5} & -6.7\times 10^{-6} & 4.7\times 10^{-7} \\
-1.8\times 10^{-6} & 2.7\times 10^{-5} & -2.6\times 10^{-6} & 1.9\times 10^{-4} & -4.0\times 10^{-3} & -3.0\times 10^{-3} & -1.8\times 10^{-5} & -1.4\times 10^{-6} & 2.2\times 10^{-5} & -2.1\times 10^{-6} & 1.5\times 10^{-4} & -3.2\times 10^{-3} & -2.7\times 10^{-3} & -1.4\times 10^{-5} & -1.1\times 10^{-6} & 1.7\times 10^{-5} & -1.6\times 10^{-6} & 1.2\times 10^{-4} & -2.6\times 10^{-3} & -2.1\times 10^{-3} & -1.0\times 10^{-5} & -9.2\times 10^{-7} & 1.4\times 10^{-5} & -1.2\times 10^{-6} & 9.4\times 10^{-5} & -2.0\times 10^{-3} & -1.6\times 10^{-3} & -7.9\times 10^{-6} & -7.3\times 10^{-7} & 1.1\times 10^{-5} & -8.8\times 10^{-7} & 7.6\times 10^{-5} & -1.1\times 10^{-3} & -1.2\times 10^{-3} & -5.2\times 10^{-6} \\
3.9\times 10^{-7} & -2.6\times 10^{-6} & 1.3\times 10^{-6} & -2.2\times 10^{-5} & 3.9\times 10^{-4} & 1.7\times 10^{-3} & 1.0\times 10^{-5} & 3.2\times 10^{-7} & -2.1\times 10^{-6} & 1.0\times 10^{-6} & -1.8\times 10^{-5} & 5.0\times 10^{-4} & 1.4\times 10^{-3} & 8.3\times 10^{-6} & 2.4\times 10^{-7} & -1.5\times 10^{-6} & 7.8\times 10^{-7} & -1.3\times 10^{-5} & 5.4\times 10^{-4} & 1.0\times 10^{-3} & 6.0\times 10^{-6} & 1.9\times 10^{-7} & -1.1\times 10^{-6} & 6.1\times 10^{-7} & -1.0\times 10^{-5} & 4.1\times 10^{-4} & 8.0\times 10^{-4} & 4.6\times 10^{-6} & 1.4\times 10^{-7} & -8.1\times 10^{-7} & 4.7\times 10^{-7} & -7.4\times 10^{-6} & 1.6\times 10^{-4} & 5.9\times 10^{-4} & 3.1\times 10^{-6} \\
-1.6\times 10^{-5} & 1.9\times 10^{-4} & -2.2\times 10^{-5} & 1.6\times 10^{-3} & -2.9\times 10^{-2} & -1.4\times 10^{-2} & -2.7\times 10^{-4} & -1.3\times 10^{-5} & 1.5\times 10^{-4} & -1.8\times 10^{-5} & 1.3\times 10^{-3} & -2.8\times 10^{-2} & -1.3\times 10^{-2} & -2.1\times 10^{-4} & -1.0\times 10^{-5} & 1.2\times 10^{-4} & -1.4\times 10^{-5} & 9.9\times 10^{-4} & -2.3\times 10^{-2} & -1.0\times 10^{-2} & -1.5\times 10^{-4} & -8.3\times 10^{-6} & 9.5\times 10^{-5} & -1.1\times 10^{-5} & 7.9\times 10^{-4} & -1.8\times 10^{-2} & -7.7\times 10^{-3} & -1.2\times 10^{-4} & -6.4\times 10^{-6} & 7.7\times 10^{-5} & -7.7\times 10^{-6} & 6.3\times 10^{-4} & -8.1\times 10^{-3} & -4.9\times 10^{-3} & -7.9\times 10^{-5} \\
2.1\times 10^{-4} & -4.0\times 10^{-3} & 3.9\times 10^{-4} & -2.9\times 10^{-2} & 6.9\times 10^{+0} & 1.3\times 10^{+0} & 6.7\times 10^{-3} & 1.4\times 10^{-4} & -3.0\times 10^{-3} & 3.2\times 10^{-4} & -2.2\times 10^{-2} & 5.5\times 10^{+0} & 1.1\times 10^{+0} & 5.1\times 10^{-3} & 9.6\times 10^{-5} & -2.2\times 10^{-3} & 2.3\times 10^{-4} & -1.6\times 10^{-2} & 4.5\times 10^{+0} & 9.7\times 10^{-1} & 3.7\times 10^{-3} & 6.0\times 10^{-5} & -1.7\times 10^{-3} & 1.7\times 10^{-4} & -1.3\times 10^{-2} & 3.7\times 10^{+0} & 8.5\times 10^{-1} & 3.0\times 10^{-3} & 3.9\times 10^{-5} & -1.4\times 10^{-3} & 1.3\times 10^{-4} & -1.1\times 10^{-2} & 2.9\times 10^{+0} & 6.7\times 10^{-1} & 2.1\times 10^{-3} \\
-2.6\times 10^{-4} & -3.0\times 10^{-3} & 1.7\times 10^{-3} & -1.4\times 10^{-2} & 1.3\times 10^{+0} & 1.7\times 10^{+1} & 8.7\times 10^{-3} & -1.9\times 10^{-4} & -2.8\times 10^{-3} & 1.3\times 10^{-3} & -1.3\times 10^{-2} & 1.1\times 10^{+0} & 1.4\times 10^{+1} & 7.1\times 10^{-3} & -1.7\times 10^{-4} & -1.5\times 10^{-3} & 9.7\times 10^{-4} & -6.8\times 10^{-3} & 1.8\times 10^{+0} & 1.1\times 10^{+1} & 4.9\times 10^{-3} & -1.2\times 10^{-4} & -1.0\times 10^{-3} & 7.6\times 10^{-4} & -4.4\times 10^{-3} & 1.6\times 10^{+0} & 9.6\times 10^{+0} & 3.2\times 10^{-3} & -10.0\times 10^{-5} & -3.8\times 10^{-4} & 5.6\times 10^{-4} & -7.6\times 10^{-4} & 1.4\times 10^{+0} & 7.9\times 10^{+0} & 1.8\times 10^{-3} \\
3.6\times 10^{-6} & -1.8\times 10^{-5} & 1.0\times 10^{-5} & -2.7\times 10^{-4} & 6.7\times 10^{-3} & 8.7\times 10^{-3} & 2.8\times 10^{-4} & 2.9\times 10^{-6} & -1.4\times 10^{-5} & 8.4\times 10^{-6} & -2.1\times 10^{-4} & 1.1\times 10^{-2} & 6.8\times 10^{-3} & 2.3\times 10^{-4} & 2.0\times 10^{-6} & -9.4\times 10^{-6} & 6.4\times 10^{-6} & -1.6\times 10^{-4} & 1.1\times 10^{-2} & 4.1\times 10^{-3} & 1.8\times 10^{-4} & 1.4\times 10^{-6} & -7.4\times 10^{-6} & 4.9\times 10^{-6} & -1.2\times 10^{-4} & 8.0\times 10^{-3} & 3.0\times 10^{-3} & 1.4\times 10^{-4} & 9.2\times 10^{-7} & -7.2\times 10^{-6} & 3.6\times 10^{-6} & -9.9\times 10^{-5} & 2.6\times 10^{-3} & 2.3\times 10^{-3} & 1.1\times 10^{-4} \\
4.5\times 10^{-7} & -1.4\times 10^{-6} & 3.2\times 10^{-7} & -1.3\times 10^{-5} & 1.4\times 10^{-4} & -1.9\times 10^{-4} & 2.9\times 10^{-6} & 4.0\times 10^{-7} & -1.3\times 10^{-6} & 2.7\times 10^{-7} & -1.1\times 10^{-5} & 2.0\times 10^{-4} & -2.5\times 10^{-5} & 2.3\times 10^{-6} & 3.2\times 10^{-7} & -1.0\times 10^{-6} & 2.1\times 10^{-7} & -9.1\times 10^{-6} & 1.4\times 10^{-4} & 4.3\times 10^{-5} & 1.3\times 10^{-6} & 2.6\times 10^{-7} & -8.2\times 10^{-7} & 1.7\times 10^{-7} & -7.1\times 10^{-6} & 7.4\times 10^{-5} & 5.1\times 10^{-5} & 6.9\times 10^{-7} & 1.9\times 10^{-7} & -6.0\times 10^{-7} & 1.2\times 10^{-7} & -5.3\times 10^{-6} & -5.2\times 10^{-5} & 9.5\times 10^{-6} & 2.4\times 10^{-7} \\
-1.5\times 10^{-6} & 2.2\times 10^{-5} & -2.1\times 10^{-6} & 1.5\times 10^{-4} & -3.0\times 10^{-3} & -2.8\times 10^{-3} & -1.4\times 10^{-5} & -1.3\times 10^{-6} & 1.9\times 10^{-5} & -1.8\times 10^{-6} & 1.3\times 10^{-4} & -2.4\times 10^{-3} & -3.0\times 10^{-3} & -1.2\times 10^{-5} & -1.0\times 10^{-6} & 1.6\times 10^{-5} & -1.4\times 10^{-6} & 1.0\times 10^{-4} & -2.0\times 10^{-3} & -2.6\times 10^{-3} & -7.6\times 10^{-6} & -8.4\times 10^{-7} & 1.2\times 10^{-5} & -1.0\times 10^{-6} & 8.4\times 10^{-5} & -1.5\times 10^{-3} & -2.0\times 10^{-3} & -5.6\times 10^{-6} & -6.2\times 10^{-7} & 9.3\times 10^{-6} & -7.7\times 10^{-7} & 6.3\times 10^{-5} & -7.7\times 10^{-4} & -1.1\times 10^{-3} & -4.0\times 10^{-6} \\
3.1\times 10^{-7} & -2.1\times 10^{-6} & 1.0\times 10^{-6} & -1.8\times 10^{-5} & 3.2\times 10^{-4} & 1.3\times 10^{-3} & 8.4\times 10^{-6} & 2.7\times 10^{-7} & -1.8\times 10^{-6} & 8.5\times 10^{-7} & -1.5\times 10^{-5} & 4.1\times 10^{-4} & 1.1\times 10^{-3} & 6.7\times 10^{-6} & 2.0\times 10^{-7} & -1.2\times 10^{-6} & 6.7\times 10^{-7} & -1.1\times 10^{-5} & 4.4\times 10^{-4} & 8.2\times 10^{-4} & 4.9\times 10^{-6} & 1.6\times 10^{-7} & -9.4\times 10^{-7} & 5.2\times 10^{-7} & -8.5\times 10^{-6} & 3.4\times 10^{-4} & 6.4\times 10^{-4} & 3.7\times 10^{-6} & 1.1\times 10^{-7} & -6.9\times 10^{-7} & 3.8\times 10^{-7} & -6.2\times 10^{-6} & 1.3\times 10^{-4} & 4.8\times 10^{-4} & 2.6\times 10^{-6} \\
-1.3\times 10^{-5} & 1.5\times 10^{-4} & -1.8\times 10^{-5} & 1.3\times 10^{-3} & -2.2\times 10^{-2} & -1.3\times 10^{-2} & -2.1\times 10^{-4} & -1.1\times 10^{-5} & 1.3\times 10^{-4} & -1.5\times 10^{-5} & 1.1\times 10^{-3} & -2.2\times 10^{-2} & -1.3\times 10^{-2} & -1.7\times 10^{-4} & -9.0\times 10^{-6} & 1.0\times 10^{-4} & -1.2\times 10^{-5} & 8.7\times 10^{-4} & -1.8\times 10^{-2} & -1.1\times 10^{-2} & -1.2\times 10^{-4} & -7.2\times 10^{-6} & 8.3\times 10^{-5} & -8.9\times 10^{-6} & 6.9\times 10^{-4} & -1.4\times 10^{-2} & -8.3\times 10^{-3} & -9.2\times 10^{-5} & -5.3\times 10^{-6} & 6.2\times 10^{-5} & -6.6\times 10^{-6} & 5.1\times 10^{-4} & -6.0\times 10^{-3} & -4.1\times 10^{-3} & -6.7\times 10^{-5} \\
2.6\times 10^{-4} & -3.2\times 10^{-3} & 5.0\times 10^{-4} & -2.8\times 10^{-2} & 5.5\times 10^{+0} & 1.1\times 10^{+0} & 1.1\times 10^{-2} & 2.0\times 10^{-4} & -2.4\times 10^{-3} & 4.1\times 10^{-4} & -2.2\times 10^{-2} & 5.1\times 10^{+0} & 9.4\times 10^{-1} & 8.4\times 10^{-3} & 1.4\times 10^{-4} & -1.8\times 10^{-3} & 3.0\times 10^{-4} & -1.6\times 10^{-2} & 4.3\times 10^{+0} & 8.6\times 10^{-1} & 6.0\times 10^{-3} & 9.8\times 10^{-5} & -1.4\times 10^{-3} & 2.3\times 10^{-4} & -1.3\times 10^{-2} & 3.4\times 10^{+0} & 7.8\times 10^{-1} & 4.6\times 10^{-3} & 5.8\times 10^{-5} & -1.1\times 10^{-3} & 1.7\times 10^{-4} & -1.0\times 10^{-2} & 2.4\times 10^{+0} & 6.5\times 10^{-1} & 3.2\times 10^{-3} \\
-1.3\times 10^{-4} & -2.7\times 10^{-3} & 1.4\times 10^{-3} & -1.3\times 10^{-2} & 1.1\times 10^{+0} & 1.4\times 10^{+1} & 6.8\times 10^{-3} & -2.5\times 10^{-5} & -3.0\times 10^{-3} & 1.1\times 10^{-3} & -1.3\times 10^{-2} & 9.4\times 10^{-1} & 1.4\times 10^{+1} & 6.4\times 10^{-3} & 1.8\times 10^{-5} & -2.2\times 10^{-3} & 8.6\times 10^{-4} & -1.1\times 10^{-2} & 1.5\times 10^{+0} & 1.2\times 10^{+1} & 1.6\times 10^{-3} & 2.0\times 10^{-5} & -1.6\times 10^{-3} & 6.7\times 10^{-4} & -7.7\times 10^{-3} & 1.3\times 10^{+0} & 9.5\times 10^{+0} & 3.9\times 10^{-6} & -2.3\times 10^{-5} & -6.0\times 10^{-4} & 5.1\times 10^{-4} & -3.1\times 10^{-3} & 1.1\times 10^{+0} & 7.1\times 10^{+0} & -1.3\times 10^{-3} \\
2.8\times 10^{-6} & -1.4\times 10^{-5} & 8.3\times 10^{-6} & -2.1\times 10^{-4} & 5.1\times 10^{-3} & 7.1\times 10^{-3} & 2.3\times 10^{-4} & 2.3\times 10^{-6} & -1.2\times 10^{-5} & 6.7\times 10^{-6} & -1.7\times 10^{-4} & 8.4\times 10^{-3} & 6.4\times 10^{-3} & 1.9\times 10^{-4} & 1.6\times 10^{-6} & -8.8\times 10^{-6} & 5.2\times 10^{-6} & -1.4\times 10^{-4} & 8.6\times 10^{-3} & 4.5\times 10^{-3} & 1.5\times 10^{-4} & 1.1\times 10^{-6} & -7.0\times 10^{-6} & 4.0\times 10^{-6} & -1.1\times 10^{-4} & 6.3\times 10^{-3} & 3.2\times 10^{-3} & 1.2\times 10^{-4} & 6.7\times 10^{-7} & -6.3\times 10^{-6} & 3.0\times 10^{-6} & -8.3\times 10^{-5} & 2.1\times 10^{-3} & 2.0\times 10^{-3} & 8.9\times 10^{-5} \\
